Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-11 paper.tex
Clarify meaning of phi^4 ~ id
Reviewer C:
  dans la partie fixslicing, je ne comprends pas l'utilité d'enchaîner
  les itérations plusieurs dizaines de fois, si 4 itérations
  correspondent plus où moins à l'identité.

>>>>

In effect, we have transformed the bitsliced round from
Section~\ref{sec:bitslicing}, which applied \coqe!phi_! in every round
over a uniform state representation, into 4 specialized rounds that
each operate over a specific layout of the state. We have thus traded
code size (specializing the round function to 4 specific layouts) for
improved run-time performance (avoiding the bit-twiddling operations
implied by \coqe!phi_!).
